\begin{acknowledgements}
In retrospect, this dissertation would not have been possible without the love, help,  and support of the wonderful people who surround me. If you're reading this, you might be one of them --- thank you!
While I could never hope to enumerate everyone who has helped me during my time at UCSD, I would be remiss if I did not at least attempt to acknowledge them. 


First and foremost, I would like to thank my academic parents (or more formally, my advisors) Stefan Savage and Geoff Voelker,
to whom I owe the most gratitude. They demonstrate the highest standards of mentorship and research excellence --- qualities that everyone seeks but so rarely finds.
Over the years, they have been a constant source of support, guidance, and inspiration, despite the tremendous amount of turbulence and uncertainty in the world. They gave me the freedom to explore my research interests, supported every research agenda I pursued, and provided a safe environment for me to make mistakes and learn from them. I could not have asked for better advisors and would not be who I am today without them. Thank you!


I also thank my committee members KC, David, and Terrance
for their invaluable feedback and suggestions on my work. KC and David patiently listened to my (sometimes poorly prepared) presentations and helped me realize that there is still much room for improvement. Terrance was similarly generous with his time and helped me see things from an economic perspective --- a viewpoint that is truly captivating and inspiring.

Besides the faculty on my committee, I want to thank other amazing faculty members in our department. I am privileged to work with Deian Stefan, Aaron Schulman, Kristen Vacarro, and Imani Munyaka, who guided me through various projects and generously shared their expertise. I am also incredibly grateful for the advice and help from Deepak Kumar, Earlence Fernandes, Alex Snoeren, Amy Ousterhout, Christian Dameff, and Lawrence Saul.

Next, I want to thank my fellow graduate students who are equally important in shaping the graduate school experience. 
I start by thanking the occupants of 3140: Gautam Akiwate, Audrey Ariniello (née Randall), Liam Arzola, Ani Canumalla, Ben ``Chongyang'' Du, Stewart Grant, Miro Haller, Katherine Izhikevich, Andrey Labunets, Elisa Luo, Ariana Mirian, Keegan Ryan, George Sullivan, Alisha Ukani, Shu-Ting Wang, Anil Yelam, and Wenyi Zhang.  
Many of you have played instrumental roles in shaping who I am. In particular, Stewart faithfully served as my guide to North American culture and introduced to me many wonderful things (climbing, camping, running, vegetarian food, just to name a few). I am grateful for the countless fond moments we have experienced together and look forward to many more to come. Miro is my Swiss counterpart with whom I share many interests and personalities. I am thankful for the classes we took together and the hours we spent in the lab, in the climbing gym, or in the ocean. Audrey let me work with her when I first arrived and was scrambling to find a project. Our first paper together ended up winning the applied research prize and being my most cited paper (lucky me!). Gautam mentored me through the early days and continues to support me throughout my PhD journey. Anil introduced tennis to me and had me over many times for delicious home-made Indian food and inspiring conversations. Keegan redefines the ceiling of intelligence and grit in a lab of high-achieving students. Elisa is a wonderful collaborator and great person to bounce ideas off of. Liam's dedication to surfing motivates me to do better every time. Ariana and Alisha demonstrate great leadership and interpersonal skills in the lab and the department, and I have learned a lot from them. Katherine and Ben organized various fun events while keeping 3140 a quiet place to work ({\selectlanguage{russian}Спасибо}!). 

In addition to 3140, I thank other students in Sysnet and CryptoSec: Reyna Abhyankar, Lixiang Ao, Arshia Arya, Alex Bellon, Nishant Bhaskar, Zac Blanco, Sunjay Cauligi, Junda Chen, Yi Won ``Paul'' Chung, Max Gao, Zhiyuan Guo, Yibo Guo, Linsong Guo, Shivani Hariprasad, Zijian He, Haochen Huang, Yutong Huang, Evan Johnson, Ryan Kosta, Seoyoung Kweon, Guo ``Vector'' Li, William Lin, Luoxi ``Rosie'' Meng, Daniel Moghimi, Eric Mugnier, Shravan Narayan, Nishit Pandya, Tyler Potyondy, Sumanth Rao, Yizhou Shan, Tianyi Shan, Bingyu Shen, Ye Shu, Vikranth Srivatsa, Adam Suhl, David Thien, Amanda Tomlinson, Chengcheng Xiang, Zesen Zhang, and Li Zhong.
Thank you for making CSE a fun place and teaching me many things over the years. Special thanks to Nishant, the OG of Sysnet, who acts like the older brother of junior students like me and is a constant source of wisdom. Thank you to our senior students who passed their graduate school wisdom to me: Vector, Chengcheng, and Bingyu. Thank you to Sumanth for delivering high-quality work on my behalf (because I am lazy) and being a collaborator I can count on; to Eric for being a great partner for practicing pool; to Rosie for showcasing how to be a thoughtful and kind person; and to Nishit, Paul, Rosie, and Ye for being great collaborators and driving my projects forward (yes, I know I am lazy).

I also had the great opportunity to get to know and befriend many amazing people across UCSD. I am particularly indebted to Lu Sun, who has unmatched work ethic and is incredibly reliable, considerate, and attentive. Lu taught me many important life lessons. Thank you for being a close friend and letting me be a close friend. I thank Hengyuan Zhang and Wenqing Tang for being great partners for all kinds of activities and tolerating my tempers every now and then during our travels. I would also like to thank those in the tennis group (big shout out to Alex Yen, Shuheng Li, Nikolai Vogler, Chris Priebe, Chester Holtz, Daniel Spokoyny, and Nithin Raghavan), the climbing group (Stewart, Miro, Keegan, Anil, Rosie, Pengrun Huang, and David Thien), the recently formed surfing group (special thanks to Seoyoung for being participant \#1 and advertising the group, and Liam, Rosie, Miro, and Max for participating), and the running club (kudos to Zac for starting the club). I would not have stayed sane without the fantastic times I spent with you all. In addition, without Jennifer Chien, Ehsan Hajyasini, and Marcus Fedarko, my times in the dance studios would have been much less fun. I also thank Danlu Chen for feeding me for free many times when we were in grad housing. Last but not least, I thank Cheng Fu, Xiaohan Fu, Hanxian Huang, Leon Li,  Minghua Liu, Rohan Mahapatra, Mingyao Shen, and Yanbo Zhou for the fun times and conversations we had.

I thank CSE staff members (Julie, Jarwyn, Tina, Tierra, Alice, and Valerie) for their help with administrative tasks. I also thank Jennifer Folkestad and Cindy Moore for their dedication to their jobs, which makes my life much easier. I thank all the visit day volunteers whom I had the privilege to work with, especially Miro Haller and Zachary Novack, for dedicating their time to make our visit day events possible. I thank the generations of Chez Bob volunteers.

My journey would have been far less fulfilling had it not extended beyond the borders of UCSD. I thank Camille Rubel for having my interests at heart, Alexandra ``Ally'' Nisenoff for throwing her CMU friends at me (now I have friends at CMU before even starting), and friends I made at or through the Living Water Bible Church in San Diego. I thank Warner Iveries, my knowledgeable and patient guitar teacher. I thank my landlords at Verano (Wendy and Jack), for being understanding and flexible, and my awesome roommates (Yage Jin, Junda Chen, Cheng Li, and Laura Odongo) who made my time at home a joy. I thank my PT Catherine ``Cathy'' Burgess for fixing my knee (twice!) and making every session enjoyable (you are the best!). I thank my friends' amazing plus-ones who made me feel welcome: Spandana Potineni, Camille Moore, and Trent Gomberg.
I thank the lifeguards on various beaches who allow us to surf with peace of mind, especially the person who rescued me when I was caught in a rip current. 


I am also grateful to have an incredible network of friends, collaborators, and mentors who have helped me on various occasions, including Damon McCoy from NYU (my awesome summer intern advisor), Liz Izhikevich from UCLA, Shravan Narayan from UT Austin, David Kohlbrenner from UW, Weijia He from the University of Southampton, Weitong Li from Virginia Tech, Brad Chen, Weihaw Chuang, Kurt Thomas, and Sarah Meiklejohn from Google, Blase Ur (who introduced me to research), David Cash, Grant Ho, and Ben Zhao from UChicago, my wonderful UCSD collaborators (e.g., Ramakrishna Padmanabhan and Jian Chen Yan), and my collaborators from around the world (notably Mattijs Jonker from UTwente, George Kappos from Chainalysis, Shawn Shan from Dartmouth, Mingxuan Yao from Georgia Tech, Emily Wenger from Duke, and Elijah Bouma-Sims from CMU).

I thank all the friends I have made throughout my life. Many of you are like my brothers and sisters (to be fair, I have no idea what it feels like to have a sibling), who have been there for me through the ups and downs. You have witnessed the worst parts of me, yet you still choose to stay beside me for years and decades. I would not have been able to come this far without you.

I thank Anhua Chen and Yuancheng Zhu for keeping me sane during the insane days.

Finally, I thank my parents for their love and unwavering support that powered me through this journey. I love you.

% yeah i did
% \todo{double check I thanked everyone}


\end{acknowledgements}