\PassOptionsToPackage{table}{xcolor}

\documentclass[12pt]{ucsddissertation}
% mathptmx is a Times Roman look-alike (don't use the times package)
% It isn't clear if Times is required. The OGS manual lists several
% "standard fonts" but never says they need to be used.
\usepackage{mathptmx}
\usepackage[NoDate]{currvita}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage[breaklinks=true,pdfborder={0 0 0}]{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{siunitx}
\usepackage{arydshln}
\AtBeginDocument{%
	\settowidth\cvlabelwidth{\cvlabelfont 0000--0000}%
}

%commands
\newcommand{\rating}[1]{%
	\begin{tikzpicture}[x=1ex,y=1ex]
		\begin{scope}
			\clip (0,1) circle (1);
			\fill[lightgray] (-1,0) rectangle (1,#1/50);
		\end{scope}
		\draw[black, thin, radius=1] (0,1) circle;
	\end{tikzpicture}%
}

\newcommand{\partrating}{\rating{50}}
\newcommand{\thesistitle}{Security Vulnerabilities in Service Composition
}
\newcommand{\sword}{SwordBox}

\usepackage{multirow}
\usepackage{tikz}
\newcommand*\nullcirc[1][1ex]{\tikz\draw (0,0) circle (3pt);} 
\newcommand*\halfcirc[1][1ex]{%
  \begin{tikzpicture}
  \draw[fill] (0,0)-- (90:3pt) arc (90:270:3pt) -- cycle ;
  \draw (0,0) circle (3pt);
  \end{tikzpicture}}
\newcommand*\fullcirc[1][1ex]{\tikz\fill (0,0) circle (3pt);} 

\newcommand{\bil}{\textsc{b}\xspace}
\newcommand{\mil}{\textsc{m}\xspace}
\newcommand{\thou}{\textsc{k}\xspace}


\newenvironment{CompactItemize}%
  {\begin{list}{$\triangleright$}%
    {\leftmargin=\parindent \itemsep=2pt \topsep=2pt
     \parsep=0pt \partopsep=0pt}}%
  {\end{list}}
\renewcommand{\labelitemi}{$\triangleright$}
\newcommand{\offlinetool}{CrossChecked\xspace} 

\increasemargins{.1in}

% These are just for testing/examples, delete them
\usepackage{trace}
%\usepackage{showframe} % This package was just to see page margins
% \usepackage[table]{xcolor}
\usepackage{listings,multicol}
\usepackage[english]{babel}
\usepackage{blindtext}
\input{annotations}
\overfullrule=5pt
% ---

% Required information
\title{\thesistitle}
\author{Enze Liu}
\degree{Computer Science}{Doctor of Philosopy}
% Each member of the committee should be listed as Professor Foo Bar.
% If Professor is not the correct title for one, then titles should be
% omitted entirely.
\cochair{Dr. Stefan Savage}
\cochair{Dr. Geoffrey M. Voelker}
% Your committee members (other than the chairs) must be in alphabetical order
\committee{Dr. Terrance August}
\committee{Dr. KC Claffy}
\committee{Dr. David D Clark}
\degreeyear{2025}

% Start the document
\begin{document}
% Begin with frontmatter and so forth
\frontmatter
\maketitle
\makecopyright
\makesignature
% Optional
\begin{dedication}
\setsinglespacing
\raggedright % It would be better to use \RaggedRight from ragged2e
\parindent0pt\parskip\baselineskip

\textit{To Mom and Dad, who raise me as a human being; to Stefan and Geoff, who raise me as a researcher; and to everyone who believes in and invests in me --- you made me who I am today.}


% In recognition of reading this manual before beginning to format the
% doctoral dissertation or master's thesis; for following the
% instructions written herein; for consulting with OGS Academic Affairs
% Advisers; and for not relying on other completed manuscripts, this
% manual is dedicated to all graduate students about to complete the
% doctoral dissertation or master's thesis.

% In recognition that this is my one chance to use whichever
% justification, spacing, writing style, text size, and/or textfont that
% I want to while still keeping my headings and margins consistent.
\end{dedication}
% Optional
\begin{epigraph}
\vskip0pt plus.5fil
\setsinglespacing
\begin{flushright}
``It takes a village to raise a child.''\\
\vskip\baselineskip
% -Voltaire \textit{Candide}\par
- African proverb
\end{flushright}

\vfil
\begin{center}

% \noindent ``It must be considered that there is nothing more difficult to carry out, nor more
% doubtful of success, nor more dangerous to handle, than to initiate a new order of things.''

\vskip\baselineskip
% \hskip0pt plus1fil -Niccolo Machiavelli \textit{The Prince}\hskip0pt plus4fil\null

\end{center}
\vfil
``My ears had heard of you but now my eyes have seen you.''\\
\vskip\baselineskip
- Job 42:5 (\textit{NIV})

\vfil
\end{epigraph}

% Next comes the table of contents, list of figures, list of tables,
% etc. If you have code listings, you can use \listoflistings (or
% \lstlistoflistings) to have it be produced here as well. Same with
% \listofalgorithms.
\tableofcontents
\listoffigures
\listoftables

% Preface
% \begin{preface}
% \todo{Write a preface - take a look at some examples because it seems rather free form}
% Almost nothing is said in the manual about the preface. There is no
% indication about how it is to be typeset. Given that, one is forced to
% simply typeset it and hope it is accepted. It is, however, optional
% and may be omitted.
% \end{preface}

% Your fancy acks here. Keep in mind you need to ack each paper you
% use. See the examples here. In addition, each chapter ack needs to
% be repeated at the end of the relevant chapter.
\begin{acknowledgements}
Graduate school is full of challenges and uncertainty. In retrospect, I would have not been able to finish it without the help and support from the amazing people that surround me, both past and present.
% Chapter~\ref{chap:swordbox} is a partial reprint of work submitted to multiple USENIX and ACM
% conferences under the title "SwordBox: Accelerating Shared Access in RDMA-based Disaggregated
% Memory. Stewart Grant, Alex C. Snoeren. This dissertations author was the primary investigator and
% author of this paper.
% %%
% Chapter~\ref{chap:rcuckoo} is a partial reprint of work submitted to multiple USENIX conferences
% under the title "Cuckoo for Clients: Disaggregated Cuckoo Hashing. Stewart Grant, Alex C. Snoeren.
% This dissertations author was the primary investigator and author of this paper.

First and foremost, I would like to thank my academic parents (or formally, my advisors) Stefan Savage and Geoff Voelker. They are a pair of advisors that are unmatchable. They have been incredibly supportive of my career and personal decisions. I am truly grateful for their guidance and support throughout my PhD journey. I would not have made it this far without their help. I am also grateful for the opportunity to work with them on various projects, which has been an invaluable learning experience. % shielded me under while letting make mistakes safely.

I also thank my committee members KC, David, and Terrance for their time. KC and David patiently listen to my (sometimes poorly prepared) presentations, provide invaluable feedback, and help me realize that there is still much room for improvement. Terrance is very supportive and helps me see things from an economic perspective --- a viewpoint that is truly captivating and inspiring.

Besides the faculty on my committee, I want to thank other amazing faculty members in the CSE  department. I had the privilege to work with Deian Stefan, Aaron Schulman, Kristen Vacarro, and Imani Munyaka, who 
guided me through various projects and generously shared their expertise with me. I am also grateful to have received incredibly career and life advice from Deepak Kumar, Earlence Fernandes, Alex C. Snoeren, Amy Ousterhout, and Lawrence Saul.

I thank all the occupants of 3140: Gautam Akiwate, Audrey Ariniello (nee Randall), Liam Arzola, Ani Canumalla, Ben Du, Stewart Grant, Miro Haller, Katherine Izhikevich, Andrey Labunets, Elisa Luo, Ariana Mirian, Keegan Ryan, George Sullivan, Alisha Ukani, Shu-Ting Wang, Anil Yelam, and Wenyi Zhang.
Many of them have played instrumental roles in my life and deeply shaped who I am. In particular, Stewart Grant faithfully served as my guide to North American culture and introduced many wonderful things to me (climbing, camping, running, vegetarian food, just to name a few). I am grateful for the countless fond moments we have experienced together and the many more to come. Without him, I would not have been who I am today. Miro Haller is my Swiss counterpart with whom I share many common interests and hobbies. I am grateful for the classes we took together and the hours we spent together in the lab, in the climbing gym, in the ocean, or on the running track. Audrey Ariniello let me work with her when I first arrived and was scrambling to find a research project. Our first paper together ended up winning the applied research prize and being my most cited paper. How lucky was I! Gautam Akiwate mentored me through the early days and continues to support me throughout my PhD journey. Anil Yelam introduced tennis to me and had me over many times for delicious home-made Indian food and inspiring conversions. Keegan Ryan redefines the ceiling of intelligence and grit in a lab full of high-achieving students. Elisa Luo is a wonderful collaborator and great person to bounce ideas off of. Liam Arzola's dedication to surfing motivates me to do better every time. Ariana Mirian and Alisha Ukani demonstrate great leadership and human skills in the lab and the department, and I have learned a lot from them. Katherine Izhikevich and Ben Du organized various fun events while keeping 3140 a quiet, fun place to work.

I also thank my fellow students in Sysnet and CryptoSec:   Reyna Abhyankar, Lixiang Ao, Alex Bellon, Nishant Bhaskar, Zachary Blanco, Sunjay Cauligi, Junda Chen, Paul Chung, Zhiyuan Guo, Yibo Guo, Linsong Guo, Zijian He, Haochen Huang, Yutong Huang, Evan Johnson, Ryan Kosta, Seoyoung Kweon, Guo Li, William Lin, Luoxi Meng, Daniel Moghimi, Eric Mugnier, Shravan Narayan, Nishit Pandya, Tyler Potyondy, Sumanth Rao, Yizhou Shan, Tianyi Shan, Bingyu Shen, Ye Shu, Vikranth Srivatsa, Adam Suhl, David Thien, Amanda Tomlinson, Yibo Wei, Chengcheng Xiang, Zesen Zhang, Li Zhong. Thank you for making CSE a fun place to work and teaching me many things over the years. Special thanks to Nishant Bhaskar, the OG of Sysnet, who acts like the old brother of junior students like me and is a constant source of wisdom. Thank you to our senior students who passed their graduate school wisdom to me: Guo Li, Chengcheng Xiang, Bingyu Shen. Thank you to Sumanth Rao, for delivering high-quality work for me (because I am lazy) and being a collaborator I can count on, Eric Mugnier, for being a great partner for practicing pool, 
Luoxi Meng, for demonstrating how to be a thoughtful and kind person, and Paul Chung, Ye Shu, and Nishit Pandya, for being great collaborators and driving my projects forward (yes I am lazy I know).

I also had the great opportunity to befriend amazing people from CSE and other departments. Lu Sun, who redefines the meaning of hardworking, has taught me many important lessons of friendship. I am truly grateful to have her as a close friend. I also extend my gratitude to Hengyuan Zhang and his partner Wenqing Tang, for being great travel partners and tolerating my temper every now and then. I would not have stayed sane without the fantastic times I spent with the tennis group (big shout out to Shuheng Li, Alex Yen, Daniel Spokoyny, Nikolai Vogler, Chris Priebe, Nithin Raghavan), the running club (kudos to head coach Zac Blanco), and the recently formed surfing group, and in the dance studio (which would have been much less fun without Jennifer Chien, Ehsan, and Marcus).

I would not have made it had my life not extend beyond the boarder of UCSD. I thank friends like Camille Rubel, Ally Nisenoff, and friends I made from or through living water bible church. My guitar teach Warner Iveries. \\

I thank the life guards (especially the person who rescued me when i was caught in the rip current without a surfboard) on various beaches who let us surf with a peace of mind.

I also thank other people who have helped me professionally, including Liz Izhikevich from UCLA, Shravan Narayan from UT Austin, David Kohlbrenner UW, Brad Chen, Weihaw Chuang, Kurt Thomas, and Sarah Meiklejohn from Google, my past and present collaborators from UChicago, Blase Ur (my masters' advisor), David Cash, Ben Zhao, Grant Ho, the wonderful UCSD students I collaborated with (names Rama), and my collaborators from all over the world (names).

I thank CSE staff members (Tina, Tierra, Julie, and Valerie) and visit day volunteers (names) for devoting their time to make our department a better place. I also thank Jennifer Folkestad and Cindy Moore for dedication to making the students' life easier. Chez bob volunteers as well.

My supportive and understanding roommates: Yagen Jin, Mike Chen, Cheng Li, and Laura O. 

I also grateful for many of friends who have stayed with me for years if not decades.

Anhua Chen and Yuancheng Zhu kept sane during those insane days.

Finally, I thank my parents, especially my mom, for their love and unwavering support.

% Finally, I would like to thank you for reading this far and perhaps reading the rest of the dissertation. I hope you can learn something useful and share it with others. To you all, and thy happy children of tomorrow, I send my greetings.
\todo{double check I thanked everyone}


\end{acknowledgements}

% Stupid vita goes next
\begin{vita}
\noindent
\begin{cv}{}
\begin{cvlist}{}
\item[2012-2016] Bachelor of Science, Software Engineering, Beijing Institute of Technology
\item[2016-2018] Master of Science, Computer Science, University of Chicago
\item[2019-2025] Doctor of Philosophy, Computer Science, University of California San Diego

\end{cvlist}
\end{cv}

% This puts in the PUBLICATIONS header. Note that it appears inside
% the vita environment. It is optional.
\publications

\noindent \textbf{Enze Liu}, Elisa Luo, Shawn Shan, Geoffrey M. Voelker, Ben Y. Zhao, and Stefan Savage, ``Somesite I Used To Crawl: Awareness, Agency and Efficacy in Protecting Content Creators From AI Crawlers,'' in \textit{Proceedings of the ACM Internet Measurement Conference (IMC)}, 2025.\\

\noindent Alex Bellon, Miro Haller, Andrey Labunets, \textbf{Enze Liu}, and Stefan Savage, ``An Empirical Analysis on the Use and Reporting of National Security Letters,'' in \textit{Proceedings of the ACM Symposium on Computer Science and Law (CSLAW)}, 2025.\\


\noindent \textbf{Enze Liu}, George Kappos, Eric Mugnier, Luca Invernizzi, Stefan Savage, David Tao, Kurt Thomas, Geoffrey M. Voelker, and Sarah Meiklejohn, ``Give and Take: An End-To-End Investigation of Giveaway Scam Conversion Rates,'' in \textit{Proceedings of the ACM Internet Measurement Conference (IMC)}, 2024.\\

\noindent Lu Sun, Hengyuan Zhang, \textbf{Enze Liu}, Mingyang Liu, and Kristen Vaccaro, ``NewsGuesser: Using Curiosity to Reduce Selective Exposure,'' \textit{Proceedings of the ACM on Human-Computer Interaction (CSCW)}, 2024.\\

\noindent Sumanth Rao, \textbf{Enze Liu}, Grant Ho, Geoffrey M. Voelker, and Stefan Savage, ``Unfiltered: Measuring Cloud-based Email Filtering Bypasses,'' in \textit{Proceedings of the ACM Web Conference (WWW)}, 2024.\\

\noindent \textbf{Enze Liu}, Gautam Akiwate, Mattijs Jonker, Ariana Mirian, Grant Ho, Geoffrey M. Voelker, and Stefan Savage, ``Forward Pass: On the Security Implications of Email Forwarding Mechanism and Policy,'' in \textit{Proceedings of the IEEE European Symposium on Security and Privacy} (EuroS\&P), 2023.\\

\noindent \textbf{Enze Liu}, Lu Sun, Alex Bellon, Grant Ho, Geoffrey M. Voelker, Stefan Savage, and Imani N.S. Munyaka, ``Understanding the Viability of Gmail's Origin Indicator for Identifying the Sender,'' in \textit{Proceedings of the Symposium on Usable Privacy and Security (SOUPS)}, 2023.\\

\noindent \textbf{Enze Liu}, Sumanth Rao, Sam Havron, Grant Ho, Stefan Savage, Geoffrey M. Voelker, and Damon McCoy, ``No Privacy Among Spies: Assessing the Functionality and Insecurity of Consumer Android Spyware Apps,'' \textit{Proceedings on Privacy Enhancing Technologies (PoPETS)}, 2023.\\

\noindent Anil Yelam, Stewart Grant, \textbf{Enze Liu}, Radhika Niranjan Mysore, Marcos K Aguilera, Amy Ousterhout, and Alex C. Snoeren, ``Limited Access: The Truth Behind Far Memory,'' in \textit{Proceedings of the
Workshop on Resource Disaggregation and Serverless (WORDS)}, 2023.\\

\noindent Audrey Randall, \textbf{Enze Liu}, Ramakrishna Padmanabhan, Gautam Akiwate, Geoffrey M. Voelker, Stefan Savage, and Aaron Schulman, ``Home is Where the Hijacking is: Understanding DNS Interception by Residential Routers,'' in \textit{Proceedings of the ACM Internet Measurement Conference (IMC)}, 2021.\\

\noindent \textbf{Enze Liu}, Gautam Akiwate, Mattijs Jonker, Ariana Mirian, Stefan Savage, and Geoffrey M. Voelker, ``Who's Got Your Mail? Characterizing Mail Service Provider Usage,'' in \textit{Proceedings of the ACM Internet Measurement Conference (IMC)}, 2021.\\

\noindent Audrey Randall, \textbf{Enze Liu}, Gautam Akiwate, Ramakrishna Padmanabhan, Geoffrey M. Voelker, Stefan Savage, and Aaron Schzulman, ``Trufflehunter: Cache Snooping Rare Domains at Large Public DNS Resolvers,'' in \textit{Proceedings of the ACM Internet Measurement Conference (IMC)}, 2020.\\ 

\noindent \textbf{Enze Liu}, Amanda Nakanishi, Maximilian Golla, David Cash, and Blase Ur, ``Reasoning Analytically about Password-Cracking Software,'' in \textit{Proceedings of the IEEE Symposium on Security and Privacy (S\&P)}, IEEE, 2019.\\
\end{vita}



\begin{dissertationabstract} 
%%	
Systems today are complex than ever. This complexity not only makes it challenging to protect existing systems against known vulnerabilities, but also introduces unintended security vulnerabilities that do not fall within the purview of current threat models. In this thesis, I highlight how unintended security vulnerabilities can arise from both the complexity within a system and the complexity introduced by the interaction between already complex systems. Using Android API system as an example, I demonstrate how the complexity within this one system produces vulnerabilities that ultimately enable malicious apps to perform persistent and stealthy surveillance on a target device. I then show, through the case study of email forwarding, how the composition of email systems leads to vulnerabilities that allow an adversary to reliably evade email security protections. I conclude by discussing my ongoing work on cryptocurrency scams and hacks, which further illustrates how the complexity of various systems can enable both large-scale and targeted attacks that result in significant financial losses.

Nowadays, software systems are extremely complicated that are not just a simple program running on a machine. Oftentimes, it involves dozens of different pieces of software that all are talking to each other. Each piece of software will make different assumptions about how users and other pieces of software are going to use the things they expose. In practice this creates problems because an adversary does not have to play by rules and follow the assumption. I study assumptions that made these individuals pieces of software and their security implications.

My research interests are in empirically understanding and securing real-world systems, with
a particular emphasis on complex, large-scale systems whose vulnerabilities impact a broad range of users.
At the core of this work is identifying the range of unvalidated assumptions systems make and how those
assumptions may be exposed to, and thus exploitable by, attackers. While fragility in low-level code is
well-trodden ground (e.g., how invalid assumptions about array bounds can produce control flow integrity
vulnerabilities), my work focuses on how ambiguities and assumptions in higher-level services and service
protocols create their own unique set of challenges – particularly in the presence of composition. As I
show, these issues emerge in diverse contexts ranging from operating system APIs, to standard e-mail
delivery protocols, to the systems used to manage inter-blockchain financial transactions.
A simple example of such an issue is cloud-based e-mail filtering (e.g., as provided by third-party
companies such as Proofpoint or Barracuda). To deploy such a capability, one must compose an existing
email delivery service (i.e., provided by the Simple Message Transport Protocol) with a separate mail
filtering service. Thus, inbound mail must be first diverted to the filtering service which then, after
filtering must forward the e-mail to the destination email server. However, implicit in this arrangement
is that this composition is somehow enforced. If not, a malicious sender might bypass this filtering service
by simply sending messages directly to the destination server.
Thus far, it remains a challenging task to reason about service-level assumptions like this. For one,
studying these assumptions requires reasoning about aspects that are less well-specified (e.g., the sender
of an email follows the intended flow). Further complicating the issue is the composition of services
— when services are combined to create new functionality, it exposes the fragility of their underlying
assumptions, as interactions with other services can occur in unexpected ways.
My goal is to make systems more secure, transparent, and usable at the service level, especially those
that are user-facing and widely-deployed. Achieving this goal requires understanding how these systems
work in practice, which in turn requires data. To this end, I have developed a variety of tools to collect
data, such as through large-scale measurements, reverse-engineering, and user studies. I then analyze
the collected data, understand the system and various assumptions made, identify gaps between the
assumptions and reality (how systems are intended to work versus how they actually work), and reason
about the security implications of these gaps. 

\end{dissertationabstract}

% This is where the main body of your dissertation goes!
\mainmatter

% Optional Introduction
\begin{dissertationintroduction}


\textit{What should a data center server look like?} Twenty years ago, a data center operator may
have argued for the simplicity of homogeneity over optimal performance, reasoning that carefully
picked commodity hardware at a given price point would yield the best cost-performance tradeoffs and that the
performance gains of next-generation hardware would quickly erase any benefits made by specializing
servers due to Dennard scaling.

\end{dissertationintroduction}



\chapter{Forward Pass: On the Security Implications of Email Forwarding Mechanism and Policy}
\label{chap:eurosp23}
\input{papers/email/1.intro.tex}
\input{papers/email/2.background.tex}
\input{papers/email/3.forward_in_the_wild.tex}
\input{papers/email/4.assumptions.tex}
\input{papers/email/5.attacks.tex}
\input{papers/email/6.disclosure.tex}
\input{papers/email/7.mitigation_and_discussion.tex}
\input{papers/email/8.conclusion.tex}

\chapter{No Privacy Among Spies: Assessing the Functionality and Insecurity of Consumer Android Spyware Apps}
\label{chap:pets23}
\input{papers/android/intro}
\input{papers/android/meth}
\input{papers/android/api}
\input{papers/android/spyware_data_protection}
\input{papers/android/related}
\input{papers/android/code}
\input{papers/android/discussion}
\input{papers/android/conclusion}

\chapter{Count of Monte Crypto: Accounting-based Defenses for Cross-Chain Bridges}
\label{chap:bridge}


\input{papers/bridge/intro}
\input{papers/bridge/bg}
\input{papers/bridge/meth}
\input{papers/bridge/dataset}
\input{papers/bridge/results}
\input{papers/bridge/online}
\input{papers/bridge/arch}
\input{papers/bridge/related}
\input{papers/bridge/ethics}
\input{papers/bridge/discussion}


\chapter{Conclusion}

This dissertation explores the problems and solutions for sharing disaggregated memory. The high
access latency and extreme cost of contention in far-memory over RDMA cause many data structures,
which would otherwise be efficient, to experience performance collapse. Stale caches cause
opportunistic data structures to fail under contention, and pointer-based data structures incur
additional round trips when far-memory pointers need to be resolved. Using existing techniques,
applications can be made to work, but they simply have to incur the penalties of sharing when under
contention.

\begin{center}
\textit{Data structures can be optimized for disaggregated memory by leveraging network programmability} \\
\end{center}


In this chapter we begin by summarizing the contributions of this dissertation and their
relationship to our thesis claim, and we conclude with a discussion of this works limitations paired
with future work directions in this area of research.

\section{Contributions}

In this dissertation, we have contributed to the state of the art in disaggregated memory systems by:

\begin{itemize}
    \item Demonstrating the significant performance gains achievable by using a programmable switch to cache the contended state of a data structure and resolve the conflicts in the network.
    \item Showing that a programmable switch can reduce the instruction-level bottlenecks of RDMA atomic operations.
    \item Demonstrating that through locality optimizations locks can be fit into a small amount of NIC memory.
    \item Showing that RDMA-verbs are well suited for locality optimized data structures.
\end{itemize}

We believe that these contributions are significant stepping stones towards the design of future
efficient disaggregated systems. In the case of {\sword}, which demonstrated acceleration on
list appends, it could be adapted to other data structures with similar properties, for example,
log-structured systems. We believe that the insight behind RCuckoo's locality-based optimizations is
general and that many data structures could benefit from localizing their data in a similar fashion.

\section{Future Work}


Each of the works presented in this dissertation is a step towards more efficient disaggregated
systems. In this section, we speculate on future directions for this area of research based on the
limitations of the work presented here.

The future for disaggregated systems is bright. This work has demonstrated that shared remote memory
can be made efficient with programmable networking hardware and that, through careful design, data
structures can be adapted to disaggregated memory. Hopefully, future work will build on these
techniques and enable a shift towards mainstream disaggregated computing.




\appendix
% \Blinddocument
\bibliographystyle{plain} % Or whatever style you want like plainnat

\bibliography{thesis}

% Stuff at the end of the dissertation goes in the back matter
\backmatter

\end{document}
